Type Evolution in Interactive Programming Systems

### 2024-05-30 paper.tex
Tweak paragraph size

The difficulty of the problem depends on what kind of synchronization we want to support.
If all variants of the program should eventually adopt all changes (converge), the complexity
is lesser. If we allow user to apply only certain changes from other users (divergence), the
complexity is greater. A common case may be a combination of the two where types and schema
of a program should converge, but data may diverge.

>>>>

The difficulty of the problem depends on what kind of synchronization we want to support.
If all variants of the program should eventually adopt all changes (converge), the complexity
is lesser. If we allow users to apply only certain changes from other users (divergence), the
complexity is greater. A common case may be a combination of the two where types and schema
of a program converge, but data may diverge.
